Stack Safety as a Security Property

### 2020-07-03 main.tex
Added better examples for integrity and confidentiality. Second conf example coming.

@@

Figure \ref{fig:lazyex1} shows the initial states \(\mach_e\), left,
and \(\mach_e'\), right. Low confidentiality data in green is shared
between them, while high confidentiality data in red and yellow may differ.
After executing the code shown, the final states below have written different
values to address 42, represented by the black and white components.
It is allowed for address 40 to differ between the states due to the initial
variation, but address 42 changed differently between the traces, representing
a leak of data. Meanwhile \ref{fig:lazyex2}, while high confidentiality data
is read, it is overwritten before return, and the write at step 3 always writes
the same value. Yellow and red locations differ between variations only because
of the initial variation, and the rest are identical. So this example passes.

\sna{TODO: it would be nice for this to correspond at least roughly to
     the layout in the running example.}

\begin{figure}
  % H - Body
  \[
  \begin{array}{l|l|l|l|l}
    \tracerow{1}{100}{\lw ~ r_0 ~ 40}{}{Load value at 40 to $r_0$}
    \tracerow{2}{104}{\sw ~ 42 ~ r_0}{}{Store that value to 42}
    \tracerow{3}{108}{\jalr ~ \rra ~ \rra ~ 0}{}{Return}
  \end{array}
  \]

  \begin{minipage}{.49\textwidth}
    \begin{center}
      \MemoryLabel{10em}{1.5em}{40}
      \MemoryLabel{15em}{1.5em}{42}
      \memory{2}{gray}%
      \memory{4}{red}[{\makebox[0pt]{\(\HIGHSEC\)}}]%
      \memory{2}{green}[{\makebox[0pt]{\(\LOWSEC\)}}]%
      \memory{2}{gray}%
      \\
    \end{center}
  \end{minipage}
  \begin{minipage}{.49\textwidth}
    \begin{center}
      \MemoryLabel{10em}{1.5em}{40}
      \MemoryLabel{15em}{1.5em}{42}
      \memory{2}{gray}%
      \memory{4}{yellow}[{\makebox[0pt]{\(\HIGHSEC\)}}]%
      \memory{2}{green}[{\makebox[0pt]{\(\LOWSEC\)}}]%
      \memory{2}{gray}%
      \\
    \end{center}
  \end{minipage} \\
  ~\\
  ~\\
 \begin{minipage}{.49\textwidth}
    \begin{center}
      \memory{2}{gray}%
      \memory{3}{red}
      \memory{1}{black}
      \memory{2}{green}
      \memory{2}{gray}%
      \\
    \end{center}
  \end{minipage}
  \begin{minipage}{.49\textwidth}
    \begin{center}
      \memory{2}{gray}%
      \memory{3}{yellow}%
      \memory{1}{white}
      \memory{2}{green}
      \memory{2}{gray}%
      \\
    \end{center}
  \end{minipage} \\

  \caption{Failing Trace Confidentiality}
  \label{fig:lazyex1}
\end{figure}
\leo{Discuss variations in a similar manner}

\begin{figure}
  % H - Body
  \[
  \begin{array}{l|l|l|l|l}
    \tracerow{1}{100}{\lw ~ r_0 ~ 40}{}{Load value at 40 to $r_0$}
    \tracerow{2}{104}{\sw ~ 42 ~ 0}{}{Store a constant value to 42}
    \tracerow{3}{108}{\lw ~ r_0 ~ 45}{}{Overwrite $r_0$ with accessible value}
    \tracerow{4}{112}{\jalr ~ \rra ~ \rra ~ 0}{}{Return}
  \end{array}
  \]

  \begin{minipage}{.49\textwidth}
    \begin{center}
      \MemoryLabel{10em}{1.5em}{40}
      \MemoryLabel{15em}{1.5em}{42}
      \memory{2}{gray}%
      \memory{4}{red}[{\makebox[0pt]{\(\HIGHSEC\)}}]%
      \memory{2}{green}[{\makebox[0pt]{\(\LOWSEC\)}}]%
      \memory{2}{gray}%
      \\
    \end{center}
  \end{minipage}
  \begin{minipage}{.49\textwidth}
    \begin{center}
      \MemoryLabel{10em}{1.5em}{40}
      \MemoryLabel{15em}{1.5em}{42}
      \memory{2}{gray}%
      \memory{4}{yellow}[{\makebox[0pt]{\(\HIGHSEC\)}}]%
      \memory{2}{green}[{\makebox[0pt]{\(\LOWSEC\)}}]%
      \memory{2}{gray}%
      \\
    \end{center}
  \end{minipage} \\
  ~\\
  ~\\
 \begin{minipage}{.49\textwidth}
    \begin{center}
      \memory{2}{gray}%
      \memory{3}{red}
      \memory{1}{black}
      \memory{2}{green}
      \memory{2}{gray}%
      \\
    \end{center}
  \end{minipage}
  \begin{minipage}{.49\textwidth}
    \begin{center}
      \memory{2}{gray}%
      \memory{3}{yellow}%
      \memory{1}{black}
      \memory{2}{green}
      \memory{2}{gray}%
      \\
    \end{center}
  \end{minipage} \\

  \caption{Passing Confidentiality Despite Failing Integrity}
  \label{fig:lazyex2}
\end{figure}
To lift trace confidentiality to a system property, we follow the same
pattern as in stack integrity:

>>>>

For an example see Figure \ref{fig:intex}, in which {\tt h} writes its return
value to {\tt g}'s return location the stack rather than its own. That address
is high integrity (red), and so writing to it causes the property to fail.

@@

Figure \ref{fig:confex2} shows the initial states \(\mach_e\), left,
and \(\mach_e'\), right. Low confidentiality data in green is shared
between them, while high confidentiality data in red and yellow may differ.
After executing the code shown, the final states below have written different
values to address 42, represented by the black and white components.
It is allowed for address 40 to differ between the states due to the initial
variation, but address 42 changed differently between the traces, representing
a leak of data. %Meanwhile \ref{fig:lazyex2}, while high confidentiality data
%is read, it is overwritten before return, and the write at step 3 always writes
%the same value. Yellow and red locations differ between variations only because
%of the initial variation, and the rest are identical. So this example passes.

\begin{figure}
% At Call to H
% Memory Layout
\begin{center}
\MemoryLabel{4em}{2em}{0}
\MemoryLabel{21em}{2em}{99}
\MemoryLabel{61.5em}{2em}{\SP}
\memory{3}{gray}[{\makebox[0pt]{Instructions}}]%
\hspace*{3pt}
$\cdots$
\memory{1}{white}[{\makebox[0pt]{Output}}]%
  \memory{6}{red}[{\makebox[0pt]{\(\HIGHINT\)}}]%
  \memory{2}{green}[{\makebox[0pt]{\(\LOWINT\)}}]%
\memory{2}{gray}%[{\makebox[0pt]{Uninitialized}}]
~$\cdots$
\MemoryLabel{-46.5em}{0.75em}{42}
\MemoryLabel{-42.5em}{0.75em}{0}
\MemoryLabel{-38.5em}{0.75em}{0}
\MemoryLabel{-34.5em}{0.75em}{0}
\MemoryLabel{-30.5em}{0.75em}{8}
\MemoryLabel{-26.5em}{0.75em}{}
\MemoryLabel{-22.5em}{0.75em}{17}
\MemoryLabel{-18.5em}{0.75em}{0}
\\
\end{center}
% Starting Register File
\summary{40}{0}{\thepcctr}{108}{17}{?}
\setcounter{pcctr}{40}
\vspace*{0.2em}
% H - Body
\[
\begin{array}{c|c|c|c|c}
  \row{\addi ~ \rsp ~ \rsp ~ 1}{\rsp \leftarrow \rsp + 1}{\rsp \leftarrow 109}
      {Allocate for return address}
  \row{\sw ~ \rsp ~ \rra ~ \negate 1}{[\rsp - 1] \leftarrow \rra}{[108] \leftarrow 27}
      {Store return address}
  \row{\lw ~ r_4 ~ \rsp ~ \negate 3}{r_4 \leftarrow [\rsp - 3]}{r_4 \leftarrow 17}
      {Load the argument {\tt v} to $r_4$}
  \row{\addi ~ r_4 ~ r_4 ~ 1}{r_4 \leftarrow r_4 + 1}{r_4 \leftarrow 18}
      {Increment $r_4$ by 1}
  \row{\sw ~ \rsp ~ r_4 ~ \negate 5}{[\rsp - 5] \leftarrow r_4}{[103] \leftarrow 18}
      {Store $r_4$ as {\tt g}'s return value}
  \row{\lw ~ \rra ~ \rsp ~ \negate 1}{\rra \leftarrow [\rsp - 1]}{\rra \leftarrow 31}
      {Load return address}
  \row{\addi ~ \rsp ~ \rsp ~ \negate 1}{\rsp \leftarrow \rsp - 1}{\rsp \leftarrow 108}
      {Restore the stack pointer of {\tt g}}
  \row{\jalr ~ \rra ~ \rra ~ 0}{??}{PC \leftarrow 31}
      {Return to {\tt g}}
  \end{array}
\]
\begin{center}
\MemoryLabel{4em}{2em}{0}
\MemoryLabel{21em}{2em}{99}
\MemoryLabel{44em}{2em}{\SP}
\memory{3}{gray}[{\makebox[0pt]{Instructions}}]%
\hspace*{3pt}
$\cdots$
\memory{1}{white}[{\makebox[0pt]{Output}}]%
  \memory{3}{red}%
  \memory{1}{green}%
  \memory{2}{red}%
  \memory{2}{gray}%
\memory{2}{gray}%[{\makebox[0pt]{Uninitialized}}]
~$\cdots$
\MemoryLabel{-46.5em}{0.75em}{42}
\MemoryLabel{-42.5em}{0.75em}{0}
\MemoryLabel{-38.5em}{0.75em}{0}
\MemoryLabel{-34.5em}{0.75em}{18}
\MemoryLabel{-30.5em}{0.75em}{8}
\MemoryLabel{-26.5em}{0.75em}{}
\MemoryLabel{-22.5em}{0.75em}{17}
\MemoryLabel{-18.5em}{0.75em}{0}
\MemoryLabel{-16em}{0.75em}{108}
\\
\end{center}
%
  \caption{Failing Trace Integrity}
  \label{fig:intex}
\end{figure}

\begin{figure}
% At Call to H
% Memory Layout
\begin{center}
\MemoryLabel{4em}{2em}{0}
\MemoryLabel{21em}{2em}{99}
\MemoryLabel{61.5em}{2em}{\SP}
\memory{3}{gray}[{\makebox[0pt]{Instructions}}]%
\hspace*{3pt}
$\cdots$
\memory{1}{white}[{\makebox[0pt]{Output}}]%
  \memory{6}{red}[{\makebox[0pt]{\(\HIGHSEC\)}}]%
  \memory{2}{green}[{\makebox[0pt]{\(\LOWSEC\)}}]%
\memory{2}{gray}%[{\makebox[0pt]{Uninitialized}}]
~$\cdots$
\MemoryLabel{-46.5em}{0.75em}{42}
\MemoryLabel{-42.5em}{0.75em}{0}
\MemoryLabel{-38.5em}{0.75em}{0}
\MemoryLabel{-34.5em}{0.75em}{0}
\MemoryLabel{-30.5em}{0.75em}{8}
\MemoryLabel{-26.5em}{0.75em}{}
\MemoryLabel{-22.5em}{0.75em}{17}
\MemoryLabel{-18.5em}{0.75em}{0}
\\
\end{center}
% Variant
\begin{center}
\MemoryLabel{4em}{2em}{0}
\MemoryLabel{21em}{2em}{99}
\MemoryLabel{61.5em}{2em}{\SP}
\memory{3}{gray}%
\hspace*{3pt}
$\cdots$
\memory{1}{white}%
  \memory{6}{yellow}[{\makebox[0pt]{Varied}}]%
  \memory{2}{green}%
\memory{2}{gray}%[{\makebox[0pt]{Uninitialized}}]
~$\cdots$
\MemoryLabel{-46.5em}{0.75em}{?}
\MemoryLabel{-42.5em}{0.75em}{?}
\MemoryLabel{-38.5em}{0.75em}{?}
\MemoryLabel{-34.5em}{0.75em}{?}
\MemoryLabel{-30.5em}{0.75em}{?}
\MemoryLabel{-26.5em}{0.75em}{?}
\MemoryLabel{-22.5em}{0.75em}{17}
\MemoryLabel{-18.5em}{0.75em}{0}
\\
\end{center}

% Starting Register File
\summary{40}{0}{\thepcctr}{108}{17}{?}
\setcounter{pcctr}{40}
\vspace*{0.2em}
% H - Body
\[
\begin{array}{c|c|c|c|c}
  \row{\addi ~ \rsp ~ \rsp ~ 1}{\rsp \leftarrow \rsp + 1}{\rsp \leftarrow 109}
      {Allocate for return address}
  \row{\sw ~ \rsp ~ \rra ~ \negate 1}{[\rsp - 1] \leftarrow \rra}{[108] \leftarrow 27}
      {Store return address}
  \row{\lw ~ r_4 ~ 100}{r_4 \leftarrow 100}{r_4 \leftarrow 42/?}
      {Load {\tt main}'s secret {\tt x} to $r_4$}
  \row{\addi ~ r_4 ~ r_4 ~ 1}{r_4 \leftarrow r_4 + 1}{r_4 \leftarrow 43/(?+1)}
      {Increment $r_4$ by 1}
  \row{\sw ~ \rsp ~ r_4 ~ \negate 2}{[\rsp - 2] \leftarrow r_4}{[107] \leftarrow 43/(?+1)}
      {Store $r_4$ as the return value}
  \row{\lw ~ \rra ~ \rsp ~ \negate 1}{\rra \leftarrow [\rsp - 1]}{\rra \leftarrow 31}
      {Load return address}
  \row{\addi ~ \rsp ~ \rsp ~ \negate 1}{\rsp \leftarrow \rsp - 1}{\rsp \leftarrow 108}
      {Restore the stack pointer of {\tt g}}
  \row{\jalr ~ \rra ~ \rra ~ 0}{??}{PC \leftarrow 31}
      {Return to {\tt g}}
  \end{array}
\]
\begin{center}
\MemoryLabel{4em}{2em}{0}
\MemoryLabel{21em}{2em}{99}
\MemoryLabel{44em}{2em}{\SP}
\memory{3}{gray}%
\hspace*{3pt}
$\cdots$
\memory{1}{white}%
  \memory{6}{red}%
  \memory{1}{green}%
  \memory{1}{pink}%
\memory{2}{gray}%[{\makebox[0pt]{Uninitialized}}]
~$\cdots$
\MemoryLabel{-46.5em}{0.75em}{42}
\MemoryLabel{-42.5em}{0.75em}{0}
\MemoryLabel{-38.5em}{0.75em}{0}
\MemoryLabel{-34.5em}{0.75em}{0}
\MemoryLabel{-30.5em}{0.75em}{8}
\MemoryLabel{-26.5em}{0.75em}{}
\MemoryLabel{-22.5em}{0.75em}{17}
\MemoryLabel{-19em}{0.75em}{43}
\MemoryLabel{-16em}{0.75em}{108}
\\
\end{center}
%
\begin{center}
\MemoryLabel{4em}{2em}{0}
\MemoryLabel{21em}{2em}{99}
\MemoryLabel{44em}{2em}{\SP}
\memory{3}{gray}%
\hspace*{3pt}
$\cdots$
\memory{1}{white}%
  \memory{6}{yellow}%
  \memory{1}{green}%
  \memory{1}{pink}%
\memory{2}{gray}%[{\makebox[0pt]{Uninitialized}}]
~$\cdots$
\MemoryLabel{-46.5em}{0.75em}{?}
\MemoryLabel{-42.5em}{0.75em}{?}
\MemoryLabel{-38.5em}{0.75em}{?}
\MemoryLabel{-34.5em}{0.75em}{?}
\MemoryLabel{-30.5em}{0.75em}{?}
\MemoryLabel{-26.5em}{0.75em}{?}
\MemoryLabel{-22.5em}{0.75em}{17}
\MemoryLabel{-19em}{0.75em}{?}
\MemoryLabel{-16em}{0.75em}{108}
\\
\end{center}
%
  \caption{Failing Trace Confidentiality}
  \label{fig:confex2}
\end{figure}

Figure \ref{confex2} gives an example of a trace that fails trace
confidentiality. At instruction 42, {\tt h} reads {\tt x} from {\tt main}.
Since {\tt x}, at address 100, is high confidentiality (red) the variant
may have a different value (yellow). So both \(r_4\) and address 107
differ in the final state between the original trace and the variant one,
failing the ending condition of trace confidentiality.

To lift trace confidentiality to a system property, we follow the same
pattern as in stack integrity:
